Methodology for Assessing the State of the Practice for Domain X

### 2020-10-23 StateOfPractice/Methodology/Methodology.tex
updated Section 2 Research Questions of Methodology, actions by devs

\begin{enumerate}
\item What are the artifacts that current software packages consist of? 
\item What tools are used by current software packages?
\item What principles, processes, and methodologies are used in the development of current software packages?
\item What are the pain points for developers working on SCS projects? What aspects of the existing processes, methodologies and tools do they consider could potentially be improved? What processes, methodologies and tools have they changed to reduce obstacles?
\item For research software developers, what specific actions are taken to address the following:\pmi{to do: reverse engineer from questions to developers; might remove or completely alter points below}\pmi{removed attitudes as per meeting discussion}
\begin{enumerate}
\item sustainability?\pmi{meeting discussion did consider removing this}
\item usability?
\item modifiability?\pmi{SS comment in issue 57: I think we want to keep modifiability in the list. The reasons you have listed are good reasons. Also, modifiability is such an important software quality, especially when it comes to having a good software development process.}
\end{enumerate} 
\item How does software designated as high quality by this methodology compare with top rated software by the community? \pmi{review}
\end{enumerate}

>>>>

\begin{enumerate}
\item What are the artifacts that current software packages consist of? 
\item What tools are used by current software packages?
\item What principles, processes, and methodologies are used in the development of current software packages?
\item What are the pain points for developers working on SCS projects? What aspects of the existing processes, methodologies and tools do they consider could potentially be improved? What processes, methodologies and tools have they changed to reduce obstacles?
\item For research software developers, what specific actions are taken to address the following:
\begin{enumerate}
\item sustainability?\pmi{previous meeting discussion did consider removing this; I do not see any current questions to developers that best fit this quality; confirm remove or add new question to developers?}
\item usability \pmi{question 10 touches on this but will need to be reworded or broken up - ``What if any actions were taken to address usability issues?''}
\item traceability \pmi{question to developers 3}
\item modifiability \pmi{question to developers 9}
\item maintainability \pmi{question to developers 9}
\item correctness \pmi{question to developers 8}
\item understandability \pmi{question to developers 10 touches on this; need to reword question in terms of an action}
\item unambiguity \pmi{question to developers 11}
\item reproducibility \pmi{question to developers 12}
\item visibility/transparency \pmi{questions 1,3,4,5,6 build to this but a question would need to be modified to include something along the line of ``has this information been added to the documentation?''}
\end{enumerate} 
\item How does software designated as high quality by this methodology compare with top rated software by the community? \pmi{review}
\end{enumerate}
